Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2016-02-17 Paper Sigatoka - 2015.tex
2016-02-16 10pm

@@

\begin{table}[h] 
\caption{Variables used in the study} 
\label{tabla1} 
\centering
\begin{tabular}{c|c} 
\hline
\bfseries Variable & \bfseries Meaning0'0' \\ 
\hline\hline 
$T_{a_max}$ &	Max air temperature \\
$T_{a_min}$ &	Min air temperature \\
$\overline{T}_{a}$	 & Mean air temperature \\
$H$	&  Humidity \\
$H_min$ &	Min humidity \\
$H_max$	& Max humidity \\
$R$	& Solar radiation \\
$\overline{P}$	& Mean precipitation  \\
$W_max$	& Max speed wind \\
$\overline{W}$	& Mean speed wind  \\
$L_2$	& Biological warning system – Leaf 2 \\
$L_3$	& Biological warning system – Leaf 3 \\
$L_4$	& Biological warning system – Leaf 4 \\
$E_s$	& Biological warning system – Evolution Stage \\
\hline
\end{tabular} 
\end{table}

@@

Although there are many types of indicators to assess the quality of the prediction, we selected the determination coefficient $(R^2)$.

@@

@@

\item Methods: support vector regression with the kernels functions: linear, RBF (Gaussian) and sigmoid; echo state networks; ordinary least squares linear regression, ridge regression and elastic-net regression.

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item from the set $\{ \overline{T}_{a} , H, \overline{P} , \overline{W}  \}$ use the subsets with one, two or four elements. These variables are according to experts the ones having most impact on the disease development \citep{MarinVargas1995}.
\end{itemize}

@@

>>>>

%  \usepackage{epstopdf} 
%  \usepackage{epsfig}

@@

\begin{table}[h] 
\caption{Variables used in the study} 
\label{tabla1} 
\centering
\begin{tabular}{c|c} 
\hline
\bfseries Variable & \bfseries Meaning0'0' \\ 
\hline\hline 
$T_{a_{max}}$ &	Max air temperature \\
$T_{a_{min}}$ &	Min air temperature \\
$\overline{T}_{a}$	 & Mean air temperature \\
$\overline{H}$	&  Mean Humidity \\
$H_{min}$ &	Min humidity \\
$H_{max}$	& Max humidity \\
$\overline{R}$	& Mean Solar radiation \\
$P$	& Sum precipitation  \\
$W_{max}$	& Max speed wind \\
$\overline{W}$	& Mean speed wind  \\
$L_2$	& Biological warning system – Leaf 2 \\
$L_3$	& Biological warning system – Leaf 3 \\
$L_4$	& Biological warning system – Leaf 4 \\
$E_s$	& Biological warning system – Evolution Stage \\
\hline
\end{tabular} 
\end{table}

@@

Although there are many types of indicators to assess the quality of the prediction, we selected the determination coefficient $(R^2)$ and the Root Mean Square Error $(RMSE)$.

@@

$$ RMSE = \sqrt{\frac{\sum_{i=1}^{n} {(y_i-\hat{y}_i)}^2 }{n}}$$

@@

\item Methods: support vector regression with the kernels functions: linear, gaussian and sigmoid; echo state networks; ordinary least squares linear regression, ridge regression and elastic-net regression.

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P , \overline{W}  \}$ use the subsets with one, two or four elements. These variables are according to experts the ones having most impact on the disease development \citep{MarinVargas1995}.
\end{itemize}

@@

In this section we present the main results for phase.

\figurename $.$\ref{figura4} shows the best $R^2$ for each algorithm in the experiment. Results are group by farm.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_each_algortihm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura4} 
\end{figure}

\figurename $.$\ref{figura5} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_each_number_of_observation_range_in_the_patterm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura5} 
\end{figure}

\figurename $.$\ref{figura6} shows the best $R^2$ for each variables combination. Results are group by farm.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.3]{Phase_one_Best_R2_for_variables}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura6} 
\end{figure}

\figurename $.$\ref{figura7} shows the pareto frontier with respect to $R^2$ and $RMSE$. Results are group by farm.

\begin{figure}[h] 
 \centering
 \includegraphics[scale=.6]{Phase_one_R2_RMSE}
 \caption{Phase one - Pareto frontier for $R^2$ and $RMSE$} 
 \label{figura7} 
\end{figure}
